Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-03-01 paper/main.tex
Fixed the pulse energy histogram of 1274143152 so that it includes all pulses (and not just the first half of the observation, where the burst sequences are)

\begin{figure*}[t]
    \includegraphics[width=0.32\textwidth]{1226062160_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1274143152_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1275094456_nullhist.png} \\
    \includegraphics[width=0.32\textwidth]{1275172216_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1275178816_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1283104232_nullhist.png}
    \caption{The pulse energy histograms for each of the six observations, for matched-size on- and off-pulse regions of the pulse stacks. The ObsIDs are given above each plot.}
    \label{fig:nullhist}
\end{figure*}

>>>>

\begin{figure*}[t]
    \includegraphics[width=0.32\textwidth]{1226062160_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1274143152_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1275094456_nullhist.png} \\
    \includegraphics[width=0.32\textwidth]{1275172216_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1275178816_nullhist.png}
    \includegraphics[width=0.32\textwidth]{1283104232_nullhist.png}
    \caption{{\bf The pulse energy histograms for each of the six observations, for matched-size on- and off-pulse regions of the pulse stacks. The ObsIDs are given above each plot. The on-pulse histograms include all pulses, regardless of whether they were classified as nulls by the method described in the text.}}
    \label{fig:nullhist}
\end{figure*}
